The fraction of polar aligned circumbinary disks

### 2024-12-29 src/tex/ms.tex
Add more specifics to the conclusion

Our results show that $f_\text{polar}$ is heavily dependent on the underlying parameter distributions that make up a population of systems. There are some populations (e.g. low mass disks around near-circular binaries) where we expect $f_\text{polar}$ to be near zero. Other populations (e.g. low mass disks orbiting binaries with a uniform distribution of $e_\text{b}$) where our results are consistent with previous results from \citet{ceppi2024} which found $f_\text{polar}\sim 0.5$. When we look at disks with considerable mass, however, the effects of binary eccentricity are significantly weakened. A massive disk is capable of exciting Kozai-Lidov oscillations on the binary, changing its eccentricity and allowing polar orbits for much smaller (initial) values of $e_\text{b}$. We find $f_\text{polar}\rightarrow 0.37$ as 
$j\rightarrow \infty$ which is dependent on the distribution of initial mutual inclination. Increasing $j$ moves $f_\text{polar}$ towards this limit.

>>>>

Our results show that $f_\text{polar}$ is heavily dependent on the underlying parameter distributions that make up a population of systems. In general, we find for low mass disks that $f_\text{polar} \sim e_\text{b}$, and for high mass disks $f_\text{polar} \rightarrow \text{const.}$ as $j\rightarrow \infty$, with the value of the constant being 0.37 if the directions of the disk angular momentum vectors are isotropically distributed.
If we consider a population of low mass disks with a uniform distribution of $e_\text{b}$, then our results are consistent with previous results from \citet{ceppi2024} which found $f_\text{polar}\sim 0.5$.

Most of the calculations presented in this work assume that the initial disk angular momentum vector has no preference for its direction, and that the distribution is isotropic. However, we also include calculations that unsurprisingly show that $f_\text{polar}$ is reduced when disks tend to be aligned with their host at the time of formation.
